{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-08-28 documents/supplemental.tex
a

@@

@@

\begin{itemize}
	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
	\item The ideal 
	\item The assumption that the only YIG-tuned 
\end{itemize}

@@

@@

\rule{\linewidth}{0.2pt}
%
%An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
%
%
%
%This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
%
%Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
%
%However, I think this person may have missed out. Learning 
%
%So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively. I have often found that I learn greatly from working on the projects of others.
%
%We present this only as a cautionary tale in the hopes that someday I will listen.

>>>>

Both finite-element, molecular-dynamics, and stiffness-eigenvalue normal mode techniques have been used to great effect for this purpose.

@@

Many

@@

\begin{itemize}
	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
	\item The ideal 
	\item The assumption that the only commercially available oscillators in this frequency range were expensive YIG-tuned devices.
\end{itemize}

@@

\begin{quote}
With four parameters I can fit an elephant, and with five I can make him wiggle his trunk.
\end{quote}
- von Neumann

with six parameters, you can do it with only physical constants. Beware numerology.

Most passives (inductors, capacitors) companies supply S-parameters for their parts. Use them.

@@

Lesson learned: implementing safeties in hardware when possible, even in non-critical systems, can greatly speed development.

Like many microwave semiconductor HBT or pHEMT MMICs, the HMC996 amplifier requires.

Sometimes vertical integration is the wrong move. Objectively, in this case, it was simply the *wrong decision*.

%
%An expert and distinguished gentleman that we contacted regarding assistance resolving transients in our microstrip VCO stated the following:
%
%
%
%This was a perfectly sensible remark; it is almost always the case that (at X-band, no less!) a custom IC would have been needed to build a VCO.
%
%Also, if taken in the context of a tired, overworked PI getting an unsolicited email from an excessively verbose undergraduate at a different university, I hardly think I would have replied differently.
%
%However, I think this person may have missed out. Learning 
%
%So perhaps it is wise to ponder the ideas of fools for skeet; one always learns target practice, if only an example what not to do, and occasionally one learns positively. I have often found that I learn greatly from working on the projects of others.
%
%We present this only as a cautionary tale in the hopes that someday I will listen.

% This is
